2024 US Presidential Election Model

### 2024-10-20 paper/paper.qmd
committing changes to the qmd file

## Diagnostics

@@

@tbl-modelsummary presents the results of the logistic regression model predicting the winner of the 2024 US Presidential Election in each state based on polling percentages for Donald Trump and Kamala Harris. The coefficients indicate that an increase in Trump’s polling percentage (\( \beta = 8.72 \)) is positively associated with the probability of winning a state, whereas an increase in Harris’s polling percentage (\( \beta = -31.63 \)) is negatively associated with Trump’s probability of winning. The standard errors for both predictors are quite large, suggesting high variability in the estimates and possible uncertainty in the model.

>>>>

## Diagnostics
@tbl-modelsummary presents the results of the logistic regression model predicting the winner of the 2024 US Presidential Election in each state based on polling percentages for Donald Trump and Kamala Harris. The coefficients indicate that an increase in Trump’s polling percentage (\( \beta = 8.72 \)) is positively associated with the probability of winning a state, whereas an increase in Harris’s polling percentage (\( \beta = -31.63 \)) is negatively associated with Trump’s probability of winning. The standard errors for both predictors are quite large, suggesting high variability in the estimates and possible uncertainty in the model.

@@
